Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2022-04-14 doc/manuscript/ESSDmanuscript.Rmd
update figure captions
#33, #34

```{r fig_map, out.width = "15cm", echo = FALSE, fig.cap = "\\textbf{Map of sites in ForC shaded by number of records relavent to (circles) and transferred to (triangles) EFDB.} PLACEHOLDER. We need to add records transferred to EFDB. We also need to limit map to variables relavent to EFDB. It would also be good to add an underlying map of FAP ecozones"}
#this is for a two-column figure. for one-column figure, use {r, out.width = "8.3cm", echo = FALSE, fig.cap = "one column figure"}
knitr::include_graphics("figures_tables/World_Map_of_sites_with_FAO_and_IPCC_data_sent.png")
```

```{r fig_dominant_veg, out.width = "15cm", echo = FALSE, fig.cap = "\\textbf{Historgram of number of records in ForC relavent to (grey) and transferred to (black) EFDB.} PLACEHOLDER. We need to add axis labels and the two classes of records. "}
#this is for a two-column figure. for one-column figure, use {r, out.width = "8.3cm", echo = FALSE, fig.cap = "one column figure"}
knitr::include_graphics("figures_tables/Histogram_n_Relevant_and_Transferred_Records.png")
```

>>>>

```{r fig_map, out.width = "15cm", echo = FALSE, fig.cap = "\\textbf{Map of sites in ForC shaded by number of records relavent to (circles) and transferred to (triangles) EFDB.} Symbols are colored according to the number of records at each site. Underlying map shows FAO ecozones, which are coded as follows: ...."}
#this is for a two-column figure. for one-column figure, use {r, out.width = "8.3cm", echo = FALSE, fig.cap = "one column figure"}
knitr::include_graphics("figures_tables/World_Map_of_sites_with_FAO_and_IPCC_data_sent.png")
```

```{r fig_dominant_veg, out.width = "15cm", echo = FALSE, fig.cap = "\\textbf{Histograms of number of records in ForC relevant to (grey) and transferred to (black) EFDB, organized by (a) dominant vegetation type, (b) FAO ecozone, (c) continent, and (d) stand age.} Codes are as follows: .... "}
#this is for a two-column figure. for one-column figure, use {r, out.width = "8.3cm", echo = FALSE, fig.cap = "one column figure"}
knitr::include_graphics("figures_tables/Histogram_n_Relevant_and_Transferred_Records.png")
```

### 2022-04-14 doc/manuscript/ESSDmanuscript.tex
update figure captions
#33, #34

\begin{figure}
\includegraphics[width=15cm]{figures_tables/World_Map_of_sites_with_FAO_and_IPCC_data_sent} \caption{\textbf{Map of sites in ForC shaded by number of records relavent to (circles) and transferred to (triangles) EFDB.} PLACEHOLDER. We need to add records transferred to EFDB. We also need to limit map to variables relavent to EFDB. It would also be good to add an underlying map of FAP ecozones}\label{fig:fig_map}
\end{figure}

\begin{figure}
\includegraphics[width=15cm]{figures_tables/Histogram_n_Relevant_and_Transferred_Records} \caption{\textbf{Historgram of number of records in ForC relavent to (grey) and transferred to (black) EFDB.} PLACEHOLDER. We need to add axis labels and the two classes of records. }\label{fig:fig_dominant_veg}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=15cm]{figures_tables/World_Map_of_sites_with_FAO_and_IPCC_data_sent} \caption{\textbf{Map of sites in ForC shaded by number of records relavent to (circles) and transferred to (triangles) EFDB.} Symbols are colored according to the number of records at each site. Underlying map shows FAO ecozones, which are coded as follows: ....}\label{fig:fig_map}
\end{figure}

\begin{figure}
\includegraphics[width=15cm]{figures_tables/Histogram_n_Relevant_and_Transferred_Records} \caption{\textbf{Histograms of number of records in ForC relevant to (grey) and transferred to (black) EFDB, organized by (a) dominant vegetation type, (b) FAO ecozone, (c) continent, and (d) stand age.} Codes are as follows: .... }\label{fig:fig_dominant_veg}
\end{figure}
